---
title: "Run Bash Script in R and Python"
author: "Yingqi Jing"
date: "`r format(Sys.time(), '%B %e, %Y')`"
header-includes:
  - \usepackage{textcomp}
  - \renewcommand{\thefigure}{S\arabic{figure}}
  - \renewcommand{\thetable}{S\arabic{table}}
  - \renewcommand{\thesection}{S\arabic{section}}
  - \renewcommand{\thesubsection}{S\arabic{section}.\arabic{subsection}}
  - \usepackage{tocloft}
  - \settowidth{\cftsecnumwidth}{S10x}
output:
  pdf_document:
   fig_crop: true
   fig_caption: true
   latex_engine: xelatex
   toc: true
   toc_depth: 4
   number_section: true
   pandoc_args: ["--variable=lof","--variable=lot","--bibliography=/Users/jakejing/switchdrive/bib/references.bib", "--csl=/Users/jakejing/switchdrive/bib/unified-style-linguistics.csl"]
---

```{r setup, include=FALSE}
library(knitr)
library(ggplot2)
library(reticulate) # python engine
use_python('/usr/local/bin/python3')

knit_hooks$set(crop = hook_pdfcrop, pars = function(before, options, envir) {if(before) {par(family=my.font)} else NULL})
opts_chunk$set(fig.path='figures/',
               dev = 'cairo_pdf', dev.args=list(bg='transparent'), # or quartz_pdf (for lattice)
               fig.height = 5,
               fig.width = 6,
               # engine.path = list(python = '/usr/local/bin/python3'),
               # python.reticulate = T, # not necessary, if use_python() is used above
               message = F,
               warning = F,
               autodep=T,
               cache.comments=F,
               crop=T,
               comment=NA,
               pars=T)
# graphics setup:
my.font = 'Helvetica'
# ggplot
theme_set(theme_bw(base_size = 24) +
            theme(text = element_text(family = my.font),
                  plot.background = element_rect(fill = "transparent", colour = NA)))

options(width=180)
```

\clearpage

R scripts
============

In order to run the bash command, we need to use the `system()` function in R. We first need to write the command in a string or a vector of characters, and feed the command in the system function. For example, we can list and filter all the pdfs in my Documents.

```{r run the command with system function in R}
bash_command_r = paste("ls -a ~/Documents/", "|", "grep", "'pdf'")
try(system(bash_command_r, intern = TRUE, ignore.stderr = F, ignore.stdout = F))
```


Python scripts
============

In python, you need to use the `subprocess` module to run the bash commands. Of course, there is also a `os.system()` function, which can run simple command directly. For more advance usages, it is better to use the `subprocess` module. 


```{python one way of formating the command in a string}
import subprocess
cmd = "ls -a ~/Documents/|grep 'pdf'"
# Note: careful about the use of shell=True (strongly discouraged)
ps = subprocess.Popen(cmd, shell=True,stdout=subprocess.PIPE,stderr=subprocess.STDOUT)
output = ps.communicate()[0]
print(output)
```


```{python run the command with system function in python}
# Popen() function will create an instance 
# where communicate() function will return the standard output and error
c = subprocess.Popen(['ls','-a','/Users/jakejing/Documents/'], stdout = subprocess.PIPE, stderr = subprocess.PIPE)
stdout, stderr = c.communicate()

print(stdout)
print(stderr)
```


```{python subprocess check call}
subprocess.check_call(['/Users/jakejing/git/run-bash-R-Python/program.sh',"/Users/jakejing/Documents/"])
```


References
==========

